Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a  Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-08-09 analysis/paper/paper_ana_20181122.Rmd
Agrega tabla de miembros

We used multi-physics scheme to better represent the uncertainty in the model formulation within the DA system. We generated 9 different model configurations consisting of the combination of 3 moist convection schemes (Kain–Fritsch [@kain2004], Grell–Freitas [@grell2013], and Betts–Miller–Janjic [@janjic1994]) and 3 planetary boundary layer schemes (Yonsei University Scheme [@hong2006], Mellor–Yamada–Janjic Scheme [@janjic1994], and Mellor–Yamada Nakanishi Niino [@nakanishi2009]). All ensemble members use the same land-surface model (Noah-MP, @chen2001), microphysics (WRF single-moment 6–class scheme [@hong2006a]), and radiation processes (RRTMG shortwave and longwave scheme [@iacono2008]) parameterizations.

>>>>

We used multi-physics scheme to better represent the uncertainty in the model formulation within the DA system. We generated 9 different model configurations consisting of the combination of 3 moist convection schemes (Kain–Fritsch [@kain2004], Grell–Freitas [@grell2013], and Betts–Miller–Janjic [@janjic1994]) and 3 planetary boundary layer schemes (Yonsei University Scheme [@hong2006], Mellor–Yamada–Janjic Scheme [@janjic1994], and Mellor–Yamada Nakanishi Niino [@nakanishi2009]). The distribution of these schemes among the 60 ensemble members is outlined in Table \@ref(tab:miembros-desc). The multi-physics approach is also introduced in order to represent the uncertainty associated with the more relevamnt physical processes that are not resolved by the model. All ensemble members use the same land-surface model (Noah-MP, @chen2001), microphysics (WRF single-moment 6–class scheme [@hong2006a]), and radiation processes (RRTMG shortwave and longwave scheme [@iacono2008]) parameterizations.

```{r miembros-desc}
fisica %>% 
  copy() %>% 
  .[, c("Cumulus", "PBL") := tstrsplit(fisica, split = "-")] %>% 
  .[, .(mem = paste(mem, collapse = ", ")), by = .(PBL, Cumulus)] %>% 
  dcast(Cumulus ~ PBL, value.var  = "mem") %>% 
  kable(booktabs = TRUE, caption = "Generation of the 60-member RRR multi-physics ensemble as a combination of Cumulus and PBL parameterizations, and GEFS members for boundary conditions.", 
        align = "cccc") %>% 
  add_header_above(c(" " = 1, PBL = 3)) %>% 
  kable_classic_2(full_width = FALSE) %>% 
  kable_styling(font_size = 6,
                position = "center") %>% 
  column_spec(1, )
```
